Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-02-28 public/paper/pyg4ometry.tex
missing inp files for tests

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

@@

\title{Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries}

@@

\section{FLUKA to Geant4 conversion}
FLUKA geometry is based upon a limited set of primitive volumes which can be combined using logical operations. Many FLUKA primitives are infinite in extent, so 
to emulate FLUKA geometry construction large but finite extent Geant4 primitive solids are used. Table \ref{tab:Fluka2Geant4} shows the mapping between FLUKA and Geant4 objects.
An ANTLR based expression parser is used to load and comprehend the FLUKA input syntax, an example is shown in XXX. Each FLUKA body is matched to a Geant4 
solid and a FLUKA region is represented by a Geant4 CSG tree is formed using the pyg4ometry classes.

\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|} \hline
FLUKA body						& pyg4ometry class \\ \hline
RPP (Rectangular parallelepiped)			& Box \\
BOX (General rectangular parallelepiped)		& Box \\
SPH (Sphere)    					& Orb \\
RCC (Right circular cylinder)				& Tubs \\
REC (Right elliptical cylinder)				& EllipticalTube \\
TRC (Truncated Right Angle Cone)			& Cons \\
ELL (Ellipsoid of Revolution) 				& Ellipsoid \\
WED/RAW (Right Angle Wedge)		         	& ExtrudedSolid \\
ARB	(Arbitrary Convex Polyhedron)			& TessellatedSolid \\
XYP 	($X$-$Y$ Infinite half-space)			& Box \\
XZP 	($X$-$Z$ Infinite half-space)			& Box \\
YZP 	($Y$-$Z$ Infinite half-space)			& Box \\
PLA (Generic infinite half-space)			& Box \\
XCC ($X$-axis Infinite Circular Cylinder)		& Tubs \\
YCC ($Y$-axis Infinite Circular Cylinder)		& Tubs \\
ZCC 	($Z$-axis Infinite Circular Cylinder)		& Tubs \\
XEC 	($X$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
YEC 	($Y$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
ZEC ($Z$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
QUA (Quadric surface) 					& TessellatedSolid \\ \hline
\end{tabular}
\caption{FLUKA geometry directives pyg4ometry classes.} \label{tab:Fluka2Geant4}
\end{table}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\usepackage{todonotes}

@@

\title{Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries}

@@

\section{FLUKA to Geant4 conversion}
FLUKA geometry is based upon a limited set of primitives (referred to
as \textit{bodies} which can be combined using Boolean operations.  A
\textit{zone} consists of one or more bodies combined using
intersections and subtractions.  Zones may then be further combined
using union operations to form \textit{regions}, which is defined as
the combination of one or more zones as well as a material.  \todo{nested zones.}

Translating FLUKA geometry to GDML first starts with

Translating FLUKA geometry to GDML first starts with a mapping of
FLUKA bodies to GDML solids, which is shown in
Table~\ref{tab:Fluka2Geant4}.

It is notable that FLUKA makes
widespread use of primitives that are infinite in extent, where Geant4

FLUKA geometry makes widespread use of primitives that are infinite in
extent, with this feature distinguishing it most from Geant4 where all
primitives are finite.

FLUKA geometry is most distinuished from Geant4 by its use of
primitives infinite in extent.

Bodies can be combined into
\textit{zones} using intersections and subtractions, with

Bodies may be
combined into \textit{zones} intersections and subtractions, and these
zones may then be combined into \textit{regions} with union
operations.  The most important difference between Geant4 and FLUKA's
implementation of CSG is that FLUKA makes widespread use of primitives
that are infinite in extent, whereas all Geant4 primitives are finite.
Whereas some FLUKA primitives have trivial Geant4 analogues, for
example a sphere, translating the infinite bodies to Geant4 solids is
more involved.  The mapping between FLUKA bodies and Geant4 solids is
shown in Table~\ref{tab:Fluka2Geant4}.

Many FLUKA primitives are infinite in extent, so to emulate
FLUKA geometry construction large but finite extent Geant4 primitive
solids are used.  shows the mapping
between FLUKA and Geant4 objects.  An ANTLR based expression parser is
used to load and comprehend the FLUKA input syntax, an example is
shown in XXX. Each FLUKA body is matched to a Geant4 solid and a FLUKA
region is represented by a Geant4 CSG tree is formed using the
pyg4ometry classes.

\begin{table}[hbt!]
\caption{FLUKA bodies and their corresponding Geant4 solids.} \label{tab:Fluka2Geant4}
\centering
\begin{tabular}{ll} \hline
FLUKA body						& pyg4ometry class \\ \hline
RPP (Rectangular parallelepiped)			& Box \\
BOX (General rectangular parallelepiped)		& Box \\
SPH (Sphere)    					& Orb \\
RCC (Right circular cylinder)				& Tubs \\
REC (Right elliptical cylinder)				& EllipticalTube \\
TRC (Truncated Right Angle Cone)			& Cons \\
ELL (Ellipsoid of Revolution) 				& Ellipsoid \\
WED/RAW (Right Angle Wedge)		         	& ExtrudedSolid \\
ARB	(Arbitrary Convex Polyhedron)			& TessellatedSolid \\
XYP 	($X$-$Y$ Infinite half-space)			& Box \\
XZP 	($X$-$Z$ Infinite half-space)			& Box \\
YZP 	($Y$-$Z$ Infinite half-space)			& Box \\
PLA (Generic infinite half-space)			& Box \\
XCC ($X$-axis Infinite Circular Cylinder)		& Tubs \\
YCC ($Y$-axis Infinite Circular Cylinder)		& Tubs \\
ZCC 	($Z$-axis Infinite Circular Cylinder)		& Tubs \\
XEC 	($X$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
YEC 	($Y$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
ZEC ($Z$-axis Infinite Elliptical Cylinder)		& EllipticalTube \\
QUA (Quadric surface) 					& TessellatedSolid \\ \hline
\end{tabular}
\end{table}
